---
title: "Beamer in R Markdown Highlights"
author: "CMDA GTAs"
date: "11/12/2018"
output: 
  beamer_presentation:
    theme: "Hokie"
---

```{r setup, include=FALSE}
# EXAMPLE OF AN R CHUNK


# Default (global) R Chunk output settings:
knitr::opts_chunk$set(echo = FALSE)

# Recommend installing knitr library:
# library(knitr)
## Here are some other preferences for (global) R chunk outputs:
# opts_chunk$set(echo = FALSE, tidy=FALSE, comment='')
```

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
<!-- Two ways of making bulleted lists -->

- Bullet 1
- Bullet 2
- Bullet 3

**Alternative Way Using Asterics**

* Bullet 4
* Bullet 5

## Slide with R Output

<!-- SOME R CHUNK OPTIONS:
#-------------------------------------------------------------------
Include=FALSE means runs R code without displaying code
Echo=FALSE means no R code will be displayed (only output)
Eval=FALSE means R code will not be run
Results='hide' means R code runs but results will not be displayed
-->

```{r cars, echo = TRUE}
summary(cars)

x=4
y=5
x+y
```


## Table in 2 Ways

Example | Table | in | HTML
--------|-------|----|------
1 | 2  | 3 | 4

```{r kable, echo = TRUE}
knitr::kable(mtcars[1:5,1:7], caption='A Knitr Table')
```


## Slide with Plot (No Special Arguments)

```{r pressure1}
plot(pressure,las=1,pch=20)
```

## Slide with Plot (With Special Arguments)

```{r pressure2, dev.args = list(bg = 'transparent'), fig.width=4.5, fig.height=3, fig.align="center"}
## Play around with fig.width and fig.height

par(mar=c(4,4,1,1))
plot(pressure,las=1,pch=20)
```

## Insert an Image

Other languages can be accessed from R studio by:

\includegraphics[width=1in]{~/Desktop/python.png}


## Other Language Engines

Many other languages are also supported in R markdown, e.g., Python,Julia, C++, and SQL.

\footnotesize
```{r eng names, echo = TRUE}
names(knitr::knit_engines$get())
```

## Python in R Markdown

<!-- 
For Python Chunks:
knitr::opts_chunk$set(python.reticulate = FALSE)

Put this in the setup chunk for cleaner output!
-->

```{python, echo = TRUE}
x = 'Hello, CMDA students !'
print(x.split(' '))
```

For more information:

* https://bookdown.org/yihui/rmarkdown/language-engines.html

* https://blog.rstudio.com/2018/03/26/reticulate-r-interface-to-python/


<!-- ## Python graphics 

 You can draw plots using the **matplotlib** package in Python. 

```{python} 
import matplotlib.pyplot as plt 
plt.plot([0, 2, 1, 4])
plt.show() 
```  

-->
